---
title: "Regression Line and Prediction: Weight vs Mileage"
author: "Akshay"
date: "`r Sys.Date()`"
output: 
    ioslides_presentation:
        widescreen: true
        smaller: true
---

## Introduction

- This app demonstrates the relationship between car weight (in lbs) and mileage (in mpg).
- Built using the `mtcars` dataset and a linear regression model.
- Predicts mileage based on user-provided car weight.


## Dataset: mtcars

- The `mtcars` dataset is a built-in R dataset.
- Contains data on 32 car models, including:
  - Weight (`wt`) in 1000s of lbs.
  - Mileage (`mpg`) in miles per gallon.
- Used to build a regression model for prediction.



## Regression Line

Model:
```{r}
model <- lm(mpg ~ wt, data = mtcars)
```


```{r echo=FALSE}
plot(mtcars$wt, mtcars$mpg, pch = 16, col = rgb(0, 0, 0, 0.5), 
     xlab = "Weight (1000 lbs)", ylab = "Mileage (mpg)", 
     main = "Regression Line: Weight vs Mileage")
abline(model, col = "blue", lwd = 2)
```


## Demonstration


<iframe src="https://infinity-akshay.shinyapps.io/Shiny/" width="100%" height="500px" style="border:none;"></iframe>


## Conclusion

- This app provides an intuitive way to explore the relationship between car weight and mileage.
- Demonstrates the power of regression modeling in data analysis.
- Try it yourself and predict mileage for different car weights!

<br>
**Links**

- The app is hosted on [ShinyApps.io](https://infinity-akshay.shinyapps.io/Shiny/).
- The code for the app is available on [GitHub](https://github.com/InfinityAkshay/Shiny)
- The presentation is available on [Github Pages](https://infinityakshay.github.io/Shiny/)

